\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}

\title{Replicating Summary Employment Statistics from Jardim et al.\ (2022)}
\author{Your Name}
\date{\today}

\begin{document}
\maketitle

\section{The Original Paper}

Jardim, Ekaterina, Mark C. Long, Robert Plotnick, Emma van Inwegen, Jacob
Vigdor, and Hilary Wething. 2022. ``Minimum Wage Increases and Low-Wage
Employment: Evidence from Seattle.'' \textit{American Economic Journal:
Economic Policy} 14(2): 263--314.

The paper evaluates the employment and wage effects of Seattle's Minimum Wage
Ordinance, which raised the minimum wage from \$9.47 to \$11 per hour in April
2015 and to \$13 per hour in January 2016. The authors use administrative
unemployment insurance records from Washington State to directly observe hourly
wages for the entire workforce, allowing them to focus precisely on low-wage
jobs across all industries. Their empirical strategy combines simple
first-difference analysis with synthetic control and interactive fixed effects
estimators to isolate the causal effect of the ordinance from Seattle's broader
economic boom.

\section{The Result of Interest}

I replicate the summary employment statistics reported in Table 5 of Jardim
et al.\ (2022), which documents changes in jobs, hours worked, and average wages
for Seattle's locatable establishments between 2014 Q2 and 2016 Q2. The paper
reports that jobs paying under \$19 per hour declined from 92,959 to 88,431,
a reduction of 4.8\%, and that total hours worked in such jobs fell 4.5\%. This
result establishes that low-wage employment contracted in Seattle even as overall
employment expanded, motivating the synthetic control estimates that follow.

\section{Data and Methods}

The data come from the publicly available replication package deposited by
Jardim et al.\ (2022) on the ICPSR repository (project 133921). I use the file
\texttt{region\_level\_cumulative.dta}, a PUMA-by-quarter aggregated dataset
constructed from confidential unemployment insurance records. Each row
represents one Public Use Microdata Area in Washington State for one quarter,
covering 2014 Q2 through 2016 Q3.

The preprocessing script reads the raw data file, filters to the relevant
quarter range, flags Seattle PUMAs using the region indicator variable, and
aggregates across PUMAs by summing within each Seattle-by-quarter cell.
Average hourly wage rates are derived by dividing total quarterly payroll by
total quarterly hours. The cleaned dataset is saved to \texttt{temp/clean\_data.csv}.

The analysis script reads the cleaned data, extracts the baseline (2014 Q2)
and endpoint (2016 Q2) observations for Seattle, and computes the absolute and
percentage changes in jobs, hours, and wages for jobs paying under \$19 per
hour. These values are written directly to a LaTeX table fragment in
\texttt{output/tables/main\_result.tex}, which is included below.

\section{Replication Results}

\input{../output/tables/main_result.tex}

Our replication finds that jobs paying under \$19 per hour in Seattle declined
by 1,569 (1.7\%) between 2014 Q2 and 2016 Q2, and that total hours worked in
such jobs fell by 2.7\%. Average wages rose by 5.7\%. The direction of all
three findings matches the paper exactly, but the magnitudes are smaller than
those in the NBER working paper version (2017), which reports a 4.8\% decline
in jobs and 4.5\% decline in hours. This discrepancy most likely reflects the
fact that the publicly available dataset corresponds to the revised 2022
published version, which uses a refined sample compared to the 2017 draft.

\section{What I Learned}

The most straightforward aspect of this replication was the analysis step
itself. Once the data were properly loaded and aggregated, computing percentage
changes across two quarters was simple. The harder part was understanding the
data structure. The publicly available dataset is already aggregated to the
PUMA-by-quarter level, meaning the most computationally intensive work had
already been done by the original authors and cannot be fully inspected by an
outside replicator. This is an important lesson about replication packages:
what is provided is often a processed intermediate file rather than true raw
data.

Doing this replication also clarified why the paper's results differ from prior
literature. The ability to directly observe hourly wages means the treatment
group is precisely defined. A replicator working only with public data like the
Quarterly Census of Employment and Wages could not reproduce even this
descriptive table. That data limitation is the central methodological
contribution of the paper.

\begin{thebibliography}{9}
\bibitem{jardim2022}
Jardim, Ekaterina, Mark C. Long, Robert Plotnick, Emma van Inwegen, Jacob
Vigdor, and Hilary Wething. 2022. ``Minimum Wage Increases and Low-Wage
Employment: Evidence from Seattle.'' \textit{American Economic Journal:
Economic Policy} 14(2): 263--314.
\end{thebibliography}

\end{document}
